{\steve}: A hierarchical Bayesian model for Supernova Cosmology

### 2018-10-16 papers/methods/paper.tex
Tablemark
Fixing the table
Updating authors

\author{
	S.~R.~Hinton\altaffilmark{1},
	T.~M.~Davis\altaffilmark{1},
	A.~G.~Kim\altaffilmark{3},
	R.~Kessler\altaffilmark{2},
	C.~Lidman\altaffilmark{4},
	A.~M\"oller\altaffilmark{5,4},
	M.~Sako\altaffilmark{6},
	D.~Scolnic\altaffilmark{2},
	M.~Smith\altaffilmark{7} 
	\\ \vspace{0.2cm} (DES Collaboration) \\	
}

\affil{$^{1}$ School of Mathematics and Physics, University of Queensland,  Brisbane, QLD 4072, Australia}
\affil{$^{2}$ Kavli Institute for Cosmological Physics, University of Chicago, Chicago, IL 60637, USA}
\affil{$^{3}$ Lawrence Berkeley National Laboratory, 1 Cyclotron Road, Berkeley, CA 94720, USA}
\affil{$^{4}$ The Research School of Astronomy and Astrophysics, Australian National University, ACT 2601, Australia}
\affil{$^{5}$ ARC Centre of Excellence for All-sky Astrophysics (CAASTRO)}
\affil{$^{6}$ Department of Physics and Astronomy, University of Pennsylvania, Philadelphia, PA 19104, USA}
\affil{$^{7}$ School of Physics and Astronomy, University of Southampton,  Southampton, SO17 1BJ, UK}

@@

	$\delta S$ & Selection effect deviation \\
	$\langle x_1^i \rangle$ & Mean stretch nodes\\
	$\langle c^i \rangle$ & Mean color nodes\\
	$\alpha_c$ & Skewness of color population \\
	$\sigma_{M_B}$ & Population magnitude scatter \\
	$\sigma_{x_1}$ & Population stretch scatter \\
	$\sigma_{c}$ & Population color scatter \\
	$\kappa_{0}$ & Extra color dispersion\\
	$\kappa_{1}$ & Redshift-dependence of extra color dispersion\\
	\\
	& \textbf{Supernova Parameters} \\
	$m_B$ & True flux\\
	$x_1$ & True stretch \\
	$c$ & True color \\
	$z$ & True redshift \\
	$M_B$ & Derived absolute magnitude \\
	$\mu$ & Derived distance modulus \\
	\\
	& \textbf{Input Data}\textsuperscript{a} \\

@@

\begin{equation}
P(M_B, x_1, c, z | \langle M_B \rangle, \langle x_1(z) \rangle, \langle c(z) \rangle, \sigma_{m_B}, \sigma_{x_1}, \sigma_c, \alpha_c) = \notag \\
\mathcal{N}(M_B|\langle M_B \rangle, \sigma_{M_B}) \mathcal{N}(x_1 | \langle x_1(z) \rangle, \sigma_{x_1}) \mathcal{N}^{\rm{skew}}(c| \langle c(z) \rangle, \sigma_c, \alpha_c) \label{eq:l1}.
\end{equation}

@@

		Steve $\langle w \rangle$           & $-0.998\pm0.007$ & $-0.945\pm0.007$ & $-0.972\pm0.006$\\
		BBC $\langle w \rangle$             & $-1.044\pm0.006$ & $-0.978\pm0.007$ & $-1.010\pm0.005$\footnotemark\\
		$\Delta$  $\langle w \rangle$  & $+0.044\pm0.006$ & $+0.033\pm0.006$ & $+0.038\pm0.004$ \\

@@

	\enddata
	\label{tab:bulk_summary_bbc}
\end{deluxetable}
\footnotetext{This value is computed with each simulation having the same weight. It disagrees with the value provided in \citet[Table 10, row 3]{Brout18SYS} which uses inverse variance weighted averages. We do not utilise this weight because the variance is correlated with the value of $w$ due to the $\Omega_m$ prior applied in the fitting process. We note that if inverse variance weighting is applied to both datasets, they both shift by $\Delta w \approx 0.005$, and thus the predicted difference between the BBC method and {\steve} remains the same.} 
\begin{figure}
	\begin{center}
		\includegraphics[width=\columnwidth]{bulk_comparison.pdf}
	\end{center}
	\caption{Recovered $w$ for the 200 validation simulations with full treatment of statistical and systematic errors. Uncertainty on the recovered $w$ value is shown for every second data point for visual clarity.}
	\label{fig:bulk_comparison}
\end{figure}

>>>>

\author{
	S.~R.~Hinton\altaffilmark{1},
	T.~M.~Davis\altaffilmark{1},
	A.~G.~Kim\altaffilmark{2},
	D.~Brout\altaffilmark{3},
	R.~Kessler\altaffilmark{4},
	C.~Lidman\altaffilmark{5},
	A.~M\"oller\altaffilmark{6,5},
	M.~Sako\altaffilmark{3},
	D.~Scolnic\altaffilmark{4},
	M.~Smith\altaffilmark{7},
	R.~C.~Wolf\altaffilmark{8}
	\\ \vspace{0.2cm} (DES Collaboration) \\
}

\affil{$^{1}$ School of Mathematics and Physics, University of Queensland,  Brisbane, QLD 4072, Australia}
\affil{$^{2}$ Lawrence Berkeley National Laboratory, 1 Cyclotron Road, Berkeley, CA 94720, USA}
\affil{$^{3}$ Department of Physics and Astronomy, University of Pennsylvania, Philadelphia, PA 19104, USA}
\affil{$^{4}$ Kavli Institute for Cosmological Physics, University of Chicago, Chicago, IL 60637, USA}
\affil{$^{5}$ The Research School of Astronomy and Astrophysics, Australian National University, ACT 2601, Australia}
\affil{$^{6}$ ARC Centre of Excellence for All-sky Astrophysics (CAASTRO)}
\affil{$^{7}$ School of Physics and Astronomy, University of Southampton,  Southampton, SO17 1BJ, UK}
\affil{$^{8}$ Department of Physics, Stanford University, 382 Via Pueblo Mall, Stanford, CA 94305, USA}

@@

	$\delta S$ & Selection effect deviation \\
	$\langle x_1^i \rangle$ & Mean stretch nodes\\
	$\langle c^i \rangle$ & Mean color nodes\\
	$\alpha_c$ & Skewness of color population \\
	$\sigma_{M_B}$ & Population magnitude scatter \\
	$\sigma_{x_1}$ & Population stretch scatter \\
	$\sigma_{c}$ & Population color scatter \\
	$\kappa_{0}$ & Extra color dispersion\\
	$\kappa_{1}$ & Redshift-dependence of extra color dispersion\\
	\\
	& \textbf{Supernova Parameters} \\
	$m_B$ & True flux\\
	$x_1$ & True stretch \\
	$c$ & True color \\
	$z$ & True redshift \\
	$M_B$ & Derived absolute magnitude \\
	$\mu$ & Derived distance modulus \\
	\\
	& \textbf{Input Data}\tablenotemark{a} \\

@@

\begin{eqnarray}
P(M_B, x_1, c, z | \theta) &=& \mathcal{N}(M_B|\langle M_B \rangle, \sigma_{M_B}) \, \mathcal{N}(x_1 | \langle x_1(z) \rangle, \sigma_{x_1})\notag\\ &\quad\quad& \mathcal{N}^{\rm{skew}}(c| \langle c(z) \rangle, \sigma_c, \alpha_c) \label{eq:l1},
\end{eqnarray}

where $\theta = \lbrace \langle M_B \rangle, \langle x_1(z) \rangle, \langle c(z) \rangle, \sigma_{m_B}, \sigma_{x_1}, \sigma_c, \alpha_c \rbrace$ for legibility.

@@

		Steve $\langle w \rangle$           & $-0.998\pm0.007$ & $-0.945\pm0.007$ & $-0.972\pm0.006$\\
		BBC $\langle w \rangle$             & $-1.044\pm0.006$ & $-0.978\pm0.007$ & $-1.010\pm0.005$\tablenotemark{a}\\
		$\Delta$  $\langle w \rangle$  & $+0.044\pm0.006$ & $+0.033\pm0.006$ & $+0.038\pm0.004$ \\

@@

	\enddata
	\tablenotetext{a}{This value is computed with each simulation having the same weight. It disagrees with the value provided in \citet[Table 10, row 3]{Brout18SYS} which uses inverse variance weighted averages. We do not utilise this weight because the variance is correlated with the value of $w$ due to the $\Omega_m$ prior applied in the fitting process. We note that if inverse variance weighting is applied to both datasets, they both shift by $\Delta w \approx 0.005$, and thus the predicted difference between the BBC method and {\steve} remains the same.}
	\label{tab:bulk_summary_bbc}
\end{deluxetable}

\begin{figure}
	\begin{center}
		\includegraphics[width=\columnwidth]{bulk_comparison.pdf}
	\end{center}
	\caption{Recovered $w$ for the 200 validation simulations with full treatment of statistical and systematic errors. Uncertainty on the recovered $w$ value is shown for every second data point for visual clarity.}
	\label{fig:bulk_comparison}
\end{figure}
